Verification of Stencil Computations through Spatial Specifications

### 2016-07-06 paper.tex
tweak to variants

\begin{definition} The \textsf{Mult}
and \textsf{Approx} are parametric labelled variant types 
with injection function given by their definition:
%
\begin{align*}
\textsf{Mult} \, a & = \textsf{mult} \, a \mid \textsf{only} \, a \\
\textsf{Approx} \, a & = \textsf{exact} \, a \mid \textsf{lower} \, a \mid
\textsf{upper} \, a \mid \textsf{both} \, a \, a
\end{align*}
\ie{}, $\mathsf{lower}$ is an injection $\mathsf{lower} : a \rightarrow \mathsf{Approx} \, a$, and so
on. 
\label{def:mult-and-approx}
\end{definition}
%

>>>>

\begin{definition} The \textsf{Mult}
and \textsf{Approx} are parametric labelled variant (sum) types 
with injection function given by their definition:
%
\begin{align*}
\textsf{Mult} \, a & = \textsf{mult} \, a \,\mid\, \textsf{only} \, a \\
\textsf{Approx} \, a & = \textsf{exact} \, a \,\mid\, \textsf{lower} \, a \,\mid\,
\textsf{upper} \, a \,\mid\, \textsf{both} \, a \, a
\end{align*}
\ie{}, $\mathsf{lower}$ is an injection $\mathsf{lower} : a \rightarrow \mathsf{Approx} \, a$, and so
on. These are used for labelled models, and other components later in
Section~\ref{sec:analysis} with additional information.
\label{def:mult-and-approx}
\end{definition}
%
